---
title: "Quick Start"
---

---

First load swirlify:

```{r, eval=FALSE}
library(swirlify)
```

Your swirl course will be created in your current working directory. Launch the
swirl course authoring shiny app:

```{r, eval=FALSE}
swirlify("My First Lesson", "My New Course")
```

You can then start writing the first lesson in your course. The "Help" tab in
the app has a description of different question types that you can add to your
lesson. Make sure to save your lesson often! When you have a few questions
written you should try your lesson out with the "Demo Lesson" button. Once
you've finished a lesson, save the lesson and exit the app.

Now that you;ve got a lesson finished you should add it to the course 
`MANIFEST`:

```{r, eval=FALSE}
add_to_manifest()
```

To start a new lesson in this course, use the shiny authoring app again:

```{r, eval=FALSE}
swirlify("My Second Lesson", "My New Course")
```

Iterate through this process until you've written a few lessons for your course.
When you're ready to share your course you can post it on GitHub or share it as
a single file. For more information on how to share your course you should
consult our guide to [sharing your swirl course](sharing.html).