---
title: "Course Structure"
output:
  html_document:
    toc_depth: 2
    toc_float:
      collapsed: true
---

---

# Creating a New Course

Swirlify is always aware of your working directory. Make sure that your working
directory is where you want to create your new course. Once you've navigated to
an appropriate working directory use `new_lesson("[Course Name]", "[Lesson Name]")`
to create a new course. For example:

```{r, eval=FALSE}
getwd()
#> [1] "/Users/sean/"

# Don't forget to load swirlfiy!
library(swirlify)

# The name of the new lesson is 'My First Lesson'
# The name of the new course is 'My New Course'
new_lesson("My First Lesson", "My New Course")
```

Let's examine what `new_lesson()` did in the example above:

1. A new directory was created in `/Users/sean/` called `My_New_Course`.
2. A new directory was created in `/Users/sean/My_New_Course` called `My_First_Lesson`.
3. Several files were created inside of `/Users/sean/My_New_Course/My_First_Lesson`:
    - `lesson.yaml` is where you will write all of the questions for this lesson. ([Example](https://github.com/seankross/Test_Course/blob/master/Test_Lesson/lesson.yaml))
    - `initLesson.R` is an R script that is run before the lesson starts which is
    usually used to load data or set up environmental variables. ([Example](https://github.com/seankross/Test_Course/blob/master/Test_Lesson/initLesson.R))
    - `dependson.txt` is the list of R packages your lesson will require. swirl
    will install these packages if the user doesn't already have them installed. ([Example](https://github.com/seankross/Test_Course/blob/master/Test_Lesson/dependson.txt))
    - `customTests.R` is where you can write your own tests for student's answers.
    This is further discussed in [Writing Custom Tests](writing.html). ([Example](https://github.com/seankross/Test_Course/blob/master/Test_Lesson/customTests.R))
    
If everything is set up correctly then `new_lesson()` should have opened up the
new `lesson.yaml` file in a text editor. If you want to start writing your first
lesson then you should move on to reading our guide to [writing lessons](writing.html).

# Creating a New Lesson in an Existing Course

Make sure you're working directory contains the course you want to add a lesson
to. Use the `new_lesson()` function to start working on a new lesson:

```{r, eval=FALSE}
new_lesson("My Second Lesson", "My New Course")
```

# Resuming Work on an Existing Lesson

Swirlify needs to be aware of what lesson you're working on in order to properly
function. You can set the current lesson using the `set_lesson()` function:

```{r, eval=FALSE}
# If you don't provide any arguments to the function you can choose the 
# lesson.yaml file you wish to work on interactively.
set_lesson()

# Or you can explicitly specify the path to the lesson.yaml file.
set_lesson("My_New_Course/My_First_Lesson/lesson.yaml")
```

# Find Out What Lesson You're Working On

In case you lose track of what lesson you're working on, you can remind yourself:

```{r, eval=FALSE}
get_current_lesson()
```

```
You are currently working on...

Lesson: My First Lesson
Course: My New Course

This lesson is located at /Users/sean/Desktop/My_New_Course/My_First_Lesson/lesson.yaml
```